Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
added ref

---
title: 'DNA Methylation Analyses'
subtitle: '*Yaamini Venkataraman*, *Sam White*, and *Steven Roberts*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

The tutorial will cover the following: - Sequence quality assessment\
- Read alignment\
- Methylation quantification\
- File conversions\
- Potential downstream applications. Although this tutorial will not provide code for downstream applications such as differential methylation analysis, it will link to other open-access resources and examples.

@@

An example of what raw data might look like from a marine invertebrate is shown. *Note that DNA methylation patters are diverse across taxa with most invertebrates demonstrating a mosiac pattern and global methylation at CpG loci is approximately 15%.*

@@

Bismark will create the following subdirectories as outputs of the above code for genome preparation

@@

@@

# Potential downstream applications

>>>>

---
title: 'DNA Methylation Assessment'
subtitle: '*Yaamini Venkataraman*, *Sam White*, and *Steven Roberts*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

The tutorial will cover the following: \
- Sequence quality assessment\
- Read alignment\
- Methylation quantification\
- File conversions\
- Potential downstream applications. Although this tutorial will not provide code for downstream applications such as differential methylation analysis, it will link to other open-access resources and examples.

@@

@@

Bismark will create two individual folders within this directory, one for a C-\>T converted genome and the other one for the G-\>A converted genome. After creating C-\>T and G-\>A versions of the genome they will be indexed in parallel usingthe indexer. Bismark will create the following subdirectories as outputs.

@@

*Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue.* @10.7717/peerj.215

@@

# Downstream applications
